Final analysis for paper

### 2020-06-21 inst/rmd/apr2020/apr2020.Rmd
updated;

opts_knit$set(width=75)
options(xtable.comment = FALSE)
```

```{r}
classify_protection <- function(days_since){
  ifelse(days_since < 21 | days_since > (365+21),0,
         (((365+21) - days_since)/(365))
         )
}

if('prepared_data.RData' %in% dir()){
  load('prepared_data.RData')
} else {
  # Read in data
  ab <- maragra::ab
  ab_panel <- maragra::ab_panel
  bairros <- maragra::bairros
  bes <- maragra::bes
  census <- maragra::census
  clinic <- maragra::clinic
  clinic_agg <- maragra::clinic_agg
  mc <- maragra::mc
  workers <- maragra::workers

  if(!'weather.RData' %in% dir()){
    weather <- maragra::weather %>%
    mutate(precipitation = ifelse(is.na(precipitation),
                                  0,
                                  precipitation))

    # Get lags for weather
    starts <- c(15, 30, 60, 90)
    ends <- c(30, 60, 90, 120)
    for(k in 1:length(starts)){
      for(j in 1:length(ends)){
        this_start <- starts[k]
        this_end <- ends[j]
        if(this_start < this_end){
          precipitation_column_name <- paste0('precipitation_lag_', this_start, '_', this_end)
          weather[,precipitation_column_name] <- NA
          temp_column_name <- paste0('temp_lag_', this_start, '_', this_end)
        }
      }
    }
    for(i in 1:nrow(weather)){
      starts <- c(15, 30, 60, 90)
      ends <- c(30, 60, 90, 120)
      for(k in 1:length(starts)){
        for(j in 1:length(ends)){
          this_start <- starts[k]
          this_end <- ends[j]
          if(this_start < this_end){
            this_date <- weather$date[i]
            end_date <- this_date - this_start
            start_date <- this_date - this_end
            if(start_date >= min(weather$date,na.rm = TRUE) &
               end_date <= max(weather$date, na.rm = TRUE)){
              sub_data <- weather %>%
                filter(date >= start_date,
                       date <= end_date)
              precipitation_column_name <- paste0('precipitation_lag_', this_start, '_', this_end)
              weather[i,precipitation_column_name] <- mean(sub_data$precipitation, na.rm = TRUE)
              temp_column_name <- paste0('temp_lag_', this_start, '_', this_end)
              weather[i,temp_column_name] <- mean(sub_data$temp, na.rm = TRUE)
            }
          }
        }
      }
    }
    save(weather, file = 'weather.RData')
  } else {
    load('weather.RData')
  }

  # Create a dictionary to classify protection
  protection_dict <- 
    data_frame(days_since = seq(min(irs$days_since, na.rm = TRUE),
                                max(irs$days_since, na.rm = TRUE),
                                by = 1)) %>%
    mutate(protection = classify_protection(days_since))
  model_data <- 
    ab_panel %>%
    dplyr::select(oracle_number, date, absent, unidade) %>%
    left_join(irs %>% 
                dplyr::select(date, unidade, chemical, days_since), 
              by = c('unidade', 'date')) %>%
    # mutate(protection = ifelse(days_since < 21 |
    #                              days_since > (183+21) |
    #                              is.na(days_since),
    #                            0, 1)) %>%
    left_join(protection_dict) %>%
    mutate(protection = ifelse(is.na(protection), 0, protection)) %>%
    dplyr::select(-days_since) %>%
    group_by(oracle_number) %>%
    mutate(ever_sprayed = length(which(protection > 0)) > 0) %>%
  # Bring in some information on workers
    left_join(workers %>%
                dplyr::select(oracle_number,
                              permanent_or_temporary,
                              department,
                              sex,
                              # date_of_birth,
                              perm_id,
                              census_name_match_score) %>%
                # void the permids of anyone with a match score of greater than 0.25
                mutate(perm_id = ifelse(census_name_match_score > 0.25,
                                        NA,
                                        perm_id))) %>%
    # Bring in some info from the census
    left_join(census %>%
                filter(!duplicated(perm_id)) %>%
                dplyr::select(perm_id,
                              maragra_bairro,
                              maragra_fabrica,
                              education,
                              floor_material)) %>%
    # Bring in some data for weather
    left_join(weather)

    ########## !!!!!!!!!!!!!!! REMOVING 2016 for temp workers
  model_data <- model_data %>%
    filter(permanent_or_temporary == 'Permanent' |
             (permanent_or_temporary == 'Temporary' & date <= '2015-12-31'))

  # Since ad and factory are same, keep same
  model_data$field <- ifelse(model_data$department == 'Field', 
                             'Field worker',
                             'Not field worker')

  model_data <- model_data %>% 
    mutate(group = paste0(permanent_or_temporary, ' ',
                          tolower(field)))

  # Add a month column
  model_data$month_number <- add_zero(format(model_data$date, '%m'), 2)

  # Get geographic info for externality analysis
  # Get latitude / longitude into model_data
  model_data <- model_data %>%
    left_join(census %>%
                filter(!duplicated(unidade)) %>%
                dplyr::select(unidade,
                              longitude_aura,
                              latitude_aura),
              by = 'unidade')

  model_data$p <- model_data$protection

  # Centers of each bairro
  bairro_loc <- apply(coordinates(maragra::bairros_maragra_bairro), 2, mean)

  # Define function for weighting indirect protection
  weighter <- function(x){
    # out <- (1 / (x+0.01))
    # out <- 1/x
    out <- ifelse(x > 1, 0, 1-x)
    return(out)
  }

  # Define function for getting distance between houses
  overall_spatial <- model_data %>%
    group_by(lat = latitude_aura,
             lng = longitude_aura) %>%
    tally %>%
    dplyr::distinct(lat, lng, .keep_all = TRUE) %>%
    dplyr::select(-n) %>%
    filter(!is.na(lat),
           !is.na(lng)) %>%
    bind_rows(data.frame(lat = bairro_loc[2],
                         lng = bairro_loc[1])) %>%
    mutate(x = lng,
           y = lat)
  overall_spatial$overall_id <- 1:nrow(overall_spatial)
  coordinates(overall_spatial) <- ~x+y
  proj4string(overall_spatial) <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
  overall_distances <- spDists(x = overall_spatial, longlat = TRUE)

  get_protection <- function(lat, lng, protection, guess_missing = TRUE){
    # Build a dataframe
    df <- data_frame(lat, lng, protection)
    # Get id
    df$id <- 1:nrow(df)

    if(guess_missing){
      # Define function for guessing
      guess <- function(x){
        x <- x %>%
          mutate(lng = ifelse(is.na(lng), 
                              bairro_loc[1],
                              lng)) %>%

          mutate(lat = ifelse(is.na(lat), 
                              bairro_loc[2],
                              lat)) 
        return(x)
      }
      # if no geography (due to no census matching, just use average geo)
      df <- guess(df)
    }
    # save for later
    original_df <- df

    # Get unique lat/lng pairs
    df <- df %>%
      group_by(lat, lng) %>%
      summarise(protection = mean(protection, na.rm = TRUE))

    # Join to overall spatial to get distances
    df <- left_join(df, overall_spatial@data, by = c('lat', 'lng'))
    keeps <- df$overall_id
    distances <- overall_distances[keeps, keeps]

    # # Get a spatial version
    # (no longer necessary with above approach)
    # df_spatial <- df %>% filter(!is.na(lng),
    #                             !is.na(lat))
    # 
    # coordinates(df_spatial) <- ~lng+lat
    # proj4string(df_spatial) <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
    # 
    # # Get distances
    # distances <- spDists(x = df_spatial, longlat = TRUE)

    # Weight distances and return weighted protection
    out <- apply(distances, 1, function(x){
      val <- df$protection * weighter(x)
      # Infinite means distance was 0/self; remove
      val[is.infinite(val)] <- NA
      # Keep only those within a kilometer
      val <- val[x <= 1]
      mean(val, na.rm = TRUE)

      })
    right <- data.frame(lat = df$lat[!is.na(df$lat)],
                        lng = df$lng[!is.na(df$lng)],
                        herd = out)
    # Join to original df
    original_df <- original_df %>%
      left_join(right,
                by = c('lat', 'lng'))

    # Return just the protection column
    return(original_df$herd)
  }

  # For each day, get real, and hypothetical protection scores
  dates <- sort(unique(model_data$date))

  out_list <- list()
  for(i in 1:length(dates)){
    this_date <- dates[i]
    message(this_date)

    this_data <- model_data %>%
      filter(date == this_date)
    # Get protection score
    protection_scores <- get_protection(lat = this_data$latitude_aura,
                                        lng = this_data$longitude_aura,
                                        protection = this_data$protection,
                                        guess_missing = TRUE)
    this_data$herd_protection <- protection_scores
    out_list[[i]] <- this_data 
  }
  model_data <- bind_rows(out_list)

  # Plots of maps
  # Libraries
  library(tidyverse)
  library(raster)
  library(tidyr)
  library(ggplot2)
  library(RColorBrewer)
  library(broom)
  library(ggthemes)

  # Get each countries shapefile
  countries <- c('Mozambique')
  iso3s <- c('MOZ')
  for(i in 1:length(countries)){
    message('Fetching data for ', countries[i])
    x <- getData(name = 'GADM', level = 2, country = iso3s[i])
    assign(tolower(countries[i]),
           x,
           envir = .GlobalEnv)
  }

  # Define which districts are "special" -------------
  specials <- 'Manhiça'

  # Mozambique
  mozambique@data$special <- FALSE
  mozambique@data$special[mozambique@data$NAME_2 %in% specials] <- TRUE

  # Combine all data into a "long" / "tidy" format
  make_long <- function(x, region = "NAME_2"){
    shp_df <- broom::tidy(x, region = region)
    return(shp_df)
  }
  mozambique_long <- make_long(mozambique) %>% mutate(country = 'Mozambique')
  combined <- mozambique_long
  combined$special <- combined$id %in% specials
  # combined$special[!combined$special] <- NA
  # Get a map of africa to use as a background
  # from the cism package!
  africa <- cism::africa
  africa_long <- make_long(africa, region = 'COUNTRY')
  africa_long$special <- africa_long$id %in% countries

  save.image(file = 'prepared_data.RData')
}

# Remove christmas
final_data <- final_data %>%
  mutate(day_number = as.numeric(format(date, '%d')))
remove_christmas <- TRUE
if(remove_christmas){
  remove_these <- which(
    (final_data$month_number == '12' &
       final_data$day_number >= 15) |
      final_data$month_number == '01' &
      final_data$day_number <= 15

  )
}

# Prepare simulations
if('simulations.RData' %in% dir()){
  load('simulations.RData')
} else {

  time_optimize_df <-
    data.frame(date = seq(as.Date('2020-01-01'),
                          as.Date('2020-12-31'), 
                          by = 1)) %>%
    mutate(month_day = format(date, '%m-%d'))
  time_optimize_df$day_number <- (1:nrow(time_optimize_df))+20
  time_optimize_df$the_protection <- classify_protection(time_optimize_df$day_number)
  time_optimize_df <- time_optimize_df %>% dplyr::select(month_day, the_protection)

  strategies <- c('Zero', 'Max', 'Time-optimized')
  strategy_list <- list()
  for(s in 1:length(strategies)){
    dates <- sort(unique(final_data$date))
    out_list <- list()
    this_strategy <- strategies[s]

    for(i in 1:length(dates)){
      this_date <- dates[i]
      message(this_strategy, '...', this_date)

      this_data <- final_data %>%
        filter(date == this_date)

      # Define scores
      if(this_strategy == 'Zero'){
        this_data$protection <- 0
        the_protection <- rep(0, length(this_data$protection))
      }
      if(this_strategy == 'Max'){
        this_data$protection <- 1
        the_protection <- rep(1, length(this_data$protection))
      }
      if(this_strategy == 'Time-optimized'){
        this_data$month_day <- format(this_data$date, '%m-%d')
        x <- this_data %>%
          left_join(time_optimize_df)
        the_protection <- x$the_protection
        this_data$protection <- the_protection
      }
      # Get protection score
      protection_scores <- get_protection(lat = this_data$latitude_aura,
                                          lng = this_data$longitude_aura,
                                          protection = the_protection,
                                          guess_missing = TRUE)
      this_data$herd_protection <- protection_scores
      out_list[[i]] <- this_data 
    }
    out <- bind_rows(out_list)
    out$strategy <- this_strategy
    strategy_list[[s]] <- out
  }
  simulations <- bind_rows(strategy_list)
  simulations <- simulations %>%
    bind_rows(final_data %>% mutate(strategy = 'Real'))
  save(simulations, file = 'simulations.RData')
}

# Some variable things
model_data$rain_var <- model_data$precipitation_lag_15_90

# # Final data - only the ever sprayed
final_data <- model_data %>%
  filter(ever_sprayed)
#   # Temporary fix pending newer data
#   filter(date <= '2016-01-01')

# Add 5th worker type
final_data <- final_data %>%
  # Get grade
  left_join(ab_panel %>% dplyr::distinct(grade, oracle_number, date)) %>%
  mutate(year = as.numeric(format(date, '%Y'))) %>%
  left_join(wages %>% dplyr::distinct(grade, department, year, daily_usd)) 
final_data$group5 <- ifelse(is.na(final_data$daily_usd) & final_data$group != 'Temporary not field worker', 'No wage data', final_data$group)

# final_model <- felm(log(absent+1) ~ protection_var + (rain_var) | oracle_number | 0 | 0,
#                     data = final_data)
final_model <- felm(log(absent+1) ~ protection +
                      herd_protection + 
                      rain_var | oracle_number | 0 | 0,
                    data = final_data)
summary(final_model)
final_model_lm <- lm(log(absent+1) ~ protection +
                       herd_protection + (rain_var),
                     data = final_data)

library(broom)
broom::tidy(final_model)

# Prediction based on individual stuff
fake <- expand.grid(protection = seq(0, 1, 0.5),
                    herd_protection = seq(0, 1, 0.1),
                    rain_var = seq(0, 6, 1))
fe <- getfe(final_model)
predictions <- exp(predict(final_model_lm, newdata = fake, interval = 'confidence'))-1
predictions <- data.frame(predictions)
fixed_effects <- 0.067 # taken from below
fake$fit <- predictions$fit + fixed_effects
fake$lwr <- predictions$lwr + fixed_effects
fake$upr <- predictions$upr + fixed_effects

n_cols <- length(unique(fake$protection))
cols <- colorRampPalette(RColorBrewer::brewer.pal(n = 8, 'Spectral'))(n_cols)
cols[2] <- 'black'
library(maragra)
ggplot(data = fake %>% filter(rain_var == 3) %>% mutate(protection = factor(protection)),
       aes(x = herd_protection,
           y = fit,
           color = protection,
           group = protection)) +
  geom_ribbon(aes(ymin = lwr, ymax = upr,
                  fill = protection),
              color = NA,
              alpha = 0.15) +
  geom_point() +
  geom_line(alpha = 0.6) +
  scale_color_manual(name = 'Individual protection',
                     values = cols) +
  scale_fill_manual(name = 'Individual protection',
                     values = cols) +
  labs(x = 'Community protection score',
       title = 'Association between community protection, individual protection, and absenteeism',
       y = 'Estimated monthly absenteeism rate\n(Average fixed effect, 3 cm of 15-60 day prior precipitation)') + theme_maragra()

# Also make predictions by groups
worker_groups <- sort(unique(final_data$group5))
model_data_list <- model_list <- model_list_lm <- list()

for (i in 1:length(worker_groups)){
  sub_data <- final_data %>% filter(group5 == worker_groups[i])
  this_model <- felm(log(absent+1) ~ protection +
                      herd_protection + 
                      rain_var | oracle_number | 0 | 0,
                    data = sub_data)
  this_model_lm <- lm(log(absent+1) ~ protection +
                       herd_protection + (rain_var),
                     data = sub_data)
  formatted <- broom::tidy(this_model)
  formatted$group5 <- worker_groups[i]

  model_list[[i]] <- this_model
  model_list_lm[[i]] <- this_model_lm
  model_data_list[[i]] <- formatted
}
names(model_list) <- names(model_data_list) <- names(model_list_lm) <- worker_groups

# Do predictions on the different groups
fake <- expand.grid(protection = seq(0, 1, 0.5),
                    herd_protection = seq(0, 1, 0.1),
                    rain_var = 3,# seq(0, 6, 1),
                    group5 = worker_groups)
fake_list <- list()
for(i in 1:length(worker_groups)){
  this_worker_group <- worker_groups[i]
  this_model <- model_list[[i]]
  this_model_lm <- model_list_lm[[i]]
  this_fake_data <- fake %>% filter(group5 == this_worker_group)
  predictions <- exp(predict(this_model_lm, newdata = this_fake_data, interval = 'confidence'))-1
  predictions <- data.frame(predictions)
  this_fe <- getfe(this_model)
  fixed_effects <- mean(this_fe$effect)
  out <- this_fake_data
  out$fit <- predictions$fit + fixed_effects
  out$lwr <- predictions$lwr + fixed_effects
  out$upr <- predictions$upr + fixed_effects
  fake_list[[i]] <- out
}
fake <- bind_rows(fake_list)

n_cols <- length(unique(fake$protection))
cols <- colorRampPalette(RColorBrewer::brewer.pal(n = 8, 'Spectral'))(n_cols)
cols[2] <- 'black'
library(maragra)
ggplot(data = fake  %>% mutate(protection = factor(protection)),
       aes(x = herd_protection,
           y = fit,
           color = protection,
           group = protection)) +
  # geom_ribbon(aes(ymin = lwr, ymax = upr,
  #                 fill = protection),
  #             color = NA,
  #             alpha = 0.15) +
  geom_point() +
  facet_wrap(~group5) +
  geom_line(alpha = 0.6) +
  scale_color_manual(name = 'Individual protection',
                     values = cols) +
  scale_fill_manual(name = 'Individual protection',
                     values = cols) +
  labs(x = 'Community protection score',
       title = 'Association between community protection, individual protection, and absenteeism',
       y = 'Estimated monthly absenteeism rate\n(Average fixed effect, 3 cm of 15-60 day prior precipitation)') +    theme_maragra()

>>>>

opts_knit$set(width=75)
options(xtable.comment = FALSE)
source('code.R')
```

*Absences*: We observed `r nrow(ab_panel)` unique worker-days among `r length(unique(ab_panel$oracle_number))` workers. The all-period average absenteeism rate was `r round(length(which(ab_panel$absent)) / nrow(ab_panel) * 100, digits = 2)`%, though this rate varied widely as a function of worker department, sex, residence, and season (table).

# Model results (one model)

```{r}
library(broom)
broom::tidy(final_model)

# Prediction based on individual stuff
fake <- expand.grid(protection = seq(0, 1, 0.5),
                    herd_protection = seq(0, 0.6, 0.1),
                    rain_var = seq(0, 6, 1))
fe <- getfe(final_model)
predictions <- exp(predict(final_model_lm, newdata = fake, interval = 'confidence'))-1
predictions <- data.frame(predictions)
fixed_effects <- mean(fe$effect)
fake$fit <- predictions$fit + fixed_effects
fake$lwr <- predictions$lwr + fixed_effects
fake$upr <- predictions$upr + fixed_effects

n_cols <- length(unique(fake$protection))
cols <- colorRampPalette(RColorBrewer::brewer.pal(n = 8, 'Spectral'))(n_cols)
cols[2] <- 'black'
library(maragra)
ggplot(data = fake %>% filter(rain_var == 3) %>% mutate(protection = factor(protection)),
       aes(x = herd_protection,
           y = fit,
           color = protection,
           group = protection)) +
  geom_ribbon(aes(ymin = lwr, ymax = upr,
                  fill = protection),
              color = NA,
              alpha = 0.15) +
  geom_point() +
  geom_line(alpha = 0.6) +
  scale_color_manual(name = 'Individual protection',
                     values = cols) +
  scale_fill_manual(name = 'Individual protection',
                     values = cols) +
  labs(x = 'Community protection score',
       title = 'Association between community protection, individual protection, and absenteeism',
       y = 'Estimated monthly absenteeism rate\n(Average fixed effect, 3 cm of 15-60 day prior precipitation)') + theme_maragra() 
```

# Model results (segregated models)

```{r}
out_list <- list()
worker_groups <- names(model_list)
for(i in 1:length(worker_groups)){
  this_group <- worker_groups[i]
  out_list[[i]] <- broom::tidy(model_list[[i]]) %>% mutate(grp = this_group)
}
out <- bind_rows(out_list)
# Get the non segrated version too
non_seg <- broom::tidy(final_model) %>% mutate(grp = 'Non segregated')
options(scipen =  '999')
out <- out %>% bind_rows(non_seg) %>% dplyr::select(term, estimate, p.value, grp) %>%
  mutate(Type = 'Distance weighted')
```

# Radial model

```{r}
out_list <- list()
worker_groups <- names(radial_model_list)
for(i in 1:length(worker_groups)){
  this_group <- worker_groups[i]
  out_list[[i]] <- broom::tidy(radial_model_list[[i]]) %>% mutate(grp = this_group)
}
out2 <- bind_rows(out_list)
# Get the non segrated version too
non_seg <- broom::tidy(final_model_radial) %>% mutate(grp = 'Non segregated')
options(scipen =  '999')
out2 <- out2 %>% bind_rows(non_seg) %>% dplyr::select(term, estimate, p.value, grp) %>%
  mutate(Type = 'Hard threshold')

# Combined radial and hard threshold

```{r}
combined <- bind_rows(out, out2)
combined$term <- ifelse(combined$term == 'radial_herd_protection', 'herd_protection', combined$term)
combined$term <- ifelse(combined$term == 'herd_protection', 'Community protection', combined$term)
combined$term <- ifelse(combined$term == 'rain_var', 'Lagged precipitation', combined$term)
combined$term <- ifelse(combined$term == 'protection', 'Individual protection', combined$term)

combined$term <- Hmisc::capitalize(gsub('_', ' ', combined$term))
ggplot(data = combined,
       aes(x = term,
           y = estimate,
           fill = Type)) +
  facet_wrap(~grp) +
  geom_bar(stat = 'identity',
           position = position_dodge()) +
  coord_flip() +
  geom_hline(yintercept = 0) +
  theme_maragra() +
  labs(x = 'Coefficient',
       y = 'Term',
       title = 'Comparison between distance-weighted vs. hard-threshold community protection estimation')
```

```{r}

```{r}
# Also make predictions by groups
worker_groups <- names(model_list)
the_groups <- c(worker_groups, 'All')

# Do predictions on the different groups
fake <- expand.grid(protection = seq(0, 1, 0.5),
                    herd_protection = seq(0, 1, 0.1),
                    rain_var = mean(final_data$rain_var, na.rm = TRUE),
                    group = the_groups)
fake_list <- list()
for(i in 1:length(the_groups)){
  this_worker_group <- the_groups[i]
  if(this_worker_group == 'All'){
    this_model <- final_model
    this_model_lm <- final_model_lm
    this_fake_data <- fake %>% mutate(group = 'All')
  } else {
      this_model <- model_list[[i]]
    this_model_lm <- model_list_lm[[i]]
    this_fake_data <- fake %>% dplyr::filter(group == this_worker_group)
  }

  predictions <- exp(predict(this_model_lm, newdata = this_fake_data, interval = 'confidence'))-1
  predictions <- data.frame(predictions)
  this_fe <- getfe(this_model)
  fixed_effects <- mean(this_fe$effect)
  out <- this_fake_data
  out$fit <- predictions$fit + fixed_effects
  out$lwr <- predictions$lwr + fixed_effects
  out$upr <- predictions$upr + fixed_effects
  fake_list[[i]] <- out
}
fake <- bind_rows(fake_list)

n_cols <- length(unique(fake$protection))
cols <- colorRampPalette(RColorBrewer::brewer.pal(n = 8, 'Spectral'))(n_cols)
cols[2] <- 'black'
library(maragra)
ggplot(data = fake  %>% mutate(protection = factor(protection)),
       aes(x = herd_protection,
           y = fit,
           color = protection,
           group = protection)) +
  # geom_ribbon(aes(ymin = lwr, ymax = upr,
  #                 fill = protection),
  #             color = NA,
  #             alpha = 0.15) +
  geom_point() +
  facet_wrap(~group) +
  geom_line(alpha = 0.6) +
  scale_color_manual(name = 'Individual protection',
                     values = cols) +
  scale_fill_manual(name = 'Individual protection',
                     values = cols) +
  labs(x = 'Community protection score',
       title = 'Association between community protection, individual protection, and absenteeism',
       y = 'Estimated monthly absenteeism rate') +    theme_maragra()

# Wage trade-offs

```{r}
# Share of avoided absences by worker type
per_year <- predictions %>%
  filter(strategy == 'Zero') %>%
  mutate(year = as.numeric(format(date, '%Y'))) %>%
  # mutate(year_month = as.Date(paste0(format(date, '%Y-%m'), '-01'))) %>%
  group_by(date = year, 
           permanent_or_temporary) %>%
  summarise(n = n(),
            actual_absences = sum(absent),
            predicted_absences = sum(fit, na.rm = TRUE),
            actual = mean(absent, na.rm = TRUE),
            predicted = mean(fit, na.rm = TRUE)) %>%
  mutate(avoided = predicted_absences - actual_absences)

per_year = per_year %>% group_by(permanent_or_temporary) %>% summarise(avoided = mean(avoided))
per_year$p <- per_year$avoided / sum(per_year$avoided)

p_permanent <- per_year$p[per_year$permanent_or_temporary == 'Permanent']

# Cost to avoid one absence
cost <- 17.31
temporary <- seq(2, 30, by = 2)
permanent <- seq(2, 30, by = 2)
fake_wage <- expand.grid(temporary = temporary,
                         permanent = permanent)
fake_wage$z <- ((fake_wage$temporary * (1- p_permanent)) + (fake_wage$permanent * p_permanent)) 
fake_wage$f <- (fake_wage$z / cost * 100)-100
# Add the percentage of absences prevented in each group

# MAke chart of relation between wages of 2 and whether profitable or not

cols <- colorRampPalette(c('darkred', 'white', 'blue'))(200)
ggplot(data = fake_wage,
       aes(x = temporary,
           y = permanent,
           fill = f)) +
  geom_tile() +
  scale_fill_gradientn(name = '',
                   colors = cols) +
  geom_text(aes(label = paste0(round(f, digits = 1), '%'))) +
  labs(x = 'Average daily productivity value (wage): temporary workers',
       y = 'Average daily productivity value (wage): permanent workers',
       title = 'Return on investment of IRS program as a function of daily wages') +
  theme_maragra() +
  theme(legend.position = 'right')

# Make for different ratios of temporary and permanent
p_permanents <- c(0.15, 0.3, 0.45, 0.6, 0.75, 0.9)
fake_wage_list <- list()
for(i in 1:length(p_permanents)){
  p_permanent <- p_permanents[i]
    # Cost to avoid one absence
  cost <- 17.31
  temporary <- seq(2, 30, by = 2)
  permanent <- seq(2, 30, by = 2)
  fake_wage <- expand.grid(temporary = temporary,
                           permanent = permanent)
  fake_wage$z <- ((fake_wage$temporary * (1- p_permanent)) + (fake_wage$permanent * p_permanent)) 
  fake_wage$f <- (fake_wage$z / cost * 100)-100
  fake_wage_list[[i]] <- fake_wage %>% mutate(p = p_permanent)
}

fake_wage <- bind_rows(fake_wage_list)
fake_wage$p <- paste0('Percent permanent: ', fake_wage$p * 100)

ggplot(data = fake_wage,
       aes(x = temporary,
           y = permanent,
           fill = f)) +
  geom_tile() +
  scale_fill_gradientn(name = '',
                   colors = cols) +
  # geom_text(aes(label = paste0(round(f, digits = 1), '%')), size = 2) +
  labs(x = 'Average daily productivity value (wage): temporary workers',
       y = 'Average daily productivity value (wage): permanent workers',
       title = 'Return on investment of IRS program as a function of daily wages') +
  theme_maragra() +
  theme(legend.position = 'right') +
  facet_wrap(~p)
```

# Simulations

```{r}
# 
# # SIMULATIONS
# sim_data <- simulations
# sim_data$idx <- sim_data$oracle_number
# fe <- getfe(final_model)
# predictions <- exp(predict(final_model_lm, sim_data, interval = 'confidence'))-1
# predictions <- data.frame(predictions)
# # Add the fixed effects
# fixed_effects <- left_join(sim_data,
#                            data.frame(fe) %>% dplyr::select(idx, effect) %>%
#                              mutate(idx = as.character(idx))) %>%
#   .$effect
# fixed_effects <- as.numeric(fixed_effects)
# 
# predictions$fit <- predictions$fit + fixed_effects
# predictions$lwr <- predictions$lwr + fixed_effects
# predictions$upr <- predictions$upr + fixed_effects
# 
# # combine other info
# predictions <- predictions %>% bind_cols(sim_data %>% dplyr::select(date, absent, strategy, permanent_or_temporary)) %>%
#   mutate(absent = as.numeric(absent)) %>%
#   filter(!is.na(fit))
# 
# simple <- predictions %>%
#   group_by(strategy) %>%
#   summarise(n = n(),
#             actual_absences = sum(absent),
#             predicted_absences = sum(fit, na.rm = TRUE),
#             actual = mean(absent, na.rm = TRUE),
#             predicted = mean(fit, na.rm = TRUE)) %>%
#   dplyr::rename(value = predicted) %>%
#   dplyr::select(strategy, value, predicted_absences)
# 
# zero <- predictions %>%
#   filter(strategy == 'Zero') %>%
#   mutate(year = as.numeric(format(date, '%Y'))) %>%
#   group_by(year) %>%
#   summarise(n = n(),
#             actual_absences = sum(absent),
#             predicted_absences = sum(fit, na.rm = TRUE),
#             actual = mean(absent, na.rm = TRUE),
#             predicted = mean(fit, na.rm = TRUE)) %>%
#   mutate(avoided = predicted_absences - actual_absences)
# # dplyr::rename(value = predicted) %>%
# # dplyr::select(permanent_or_temporary, value, predicted_absences)
# 
# kable(simple)
# 
# # Eligible working days
# sum(zero$n)
# # Absences
# sum(zero$actual_absences)
# # Actual absence rate
# sum(zero$actual_absences) / sum(zero$n)
# # Would have observed
# sum(zero$predicted_absences)
# # Predicted - observ
# sum(zero$predicted_absences) - sum(zero$actual_absences)
#   # Overall reduction from
# sum(zero$predicted_absences) / sum(zero$n)
# # To
# sum(zero$actual_absences) / sum(zero$n)
# # Number of working days permanent vs temp
# table(predictions$permanent_or_temporary[predictions$strategy=='Real'])
# # Absences avoided among permanent workers
# predictions %>% filter(strategy == 'Zero') %>% group_by(permanent_or_temporary) %>% summarise(n = n(),
#                                                                                               actual_absences = sum(absent),
#                                                                                               predicted_absences = sum(fit, na.rm = TRUE),
#                                                                                               actual = mean(absent, na.rm = TRUE),
#                                                                                               predicted = mean(fit, na.rm = TRUE)) %>%
#   mutate(avoided = predicted_absences - actual_absences) %>%
#   # decline due to irs
#   mutate(decline = predicted - actual)
# # One absence every n days
# sum(zero$n) / sum(zero$avoided)
# # Annual reduction in absence
# mean(zero$avoided[zero$year < 2016])
# # Cost per absence avoided
# 68984 / 4183
# # Percentage of absence among permanent workers
# x = predictions %>%
#   filter(strategy == 'Zero') %>%
#   # filter(date < '2016-01-01') %>%
#   group_by(permanent_or_temporary) %>%
#   summarise(absences = sum(absent),
#             predicted = sum(fit)) %>%
#   mutate(averted = predicted - absences) %>%
#   mutate(p = averted / sum(averted))
# x
# # Weighted average cost
# y = sum(c(25, 5) * x$p)
# y
# # Cost of treatment per absence
# 22 / 80
# # Total savings per aversion
# 0.275 + y
# # Total yearly savings
# (0.275 + y) * 4183
# # Total yearly savings
# ((0.275 + y) * 4183) - 68984
# # ROI
# ((0.275 + y) * 4183) / 68984
# # Additional max strategy
# simple
# 47943-42131
# 
# ggplot(data = simple,
#        aes(x = strategy,
#            y = value)) +
#   geom_bar(stat = 'identity',
#            alpha = 0.6,
#            color = 'black') +
#   labs(y = 'Absenteeism rate',
#        x = 'Strategy') +
#   geom_label(aes(label = round(value, digits = 3)),
#              nudge_y = -0.005)

```{r}
# SIMULATIONS WITH WORKER SPECIFIC TYPE

# SIMULATIONS
sim_data <- simulations# %>%
  # # Get grade
  # left_join(ab_panel %>% dplyr::distinct(grade, oracle_number, date)) %>%
  # mutate(year = as.numeric(format(date, '%Y'))) %>%
  # left_join(wages %>% dplyr::distinct(grade, department, year, daily_usd)) 
# sim_data$group5 <- ifelse(is.na(sim_data$daily_usd) & sim_data$group != 'Temporary not field worker', 'No wage data', sim_data$group)
sim_data$idx <- sim_data$oracle_number

worker_groups <- names(model_list)
sim_list <- list()
radial_sim_list <- list()
for(i in 1:length(worker_groups)){
  message(i)
  this_worker_group <- worker_groups[i]

  this_model <- model_list[[i]]
  this_model_lm <- model_list_lm[[i]]
  this_fake_data <- sim_data %>% filter(group == this_worker_group)

  # this_radial_model <- radial_model_list[[i]]
  # this_radial_model_lm <- radial_model_list_lm[[i]]
  # this_radial_fake_data <- radial_model_data_list[[i]]

  predictions <- exp(predict(this_model_lm, newdata = this_fake_data, interval = 'confidence'))-1
  predictions <- data.frame(predictions)

  # radial_predictions <- exp(predict(this_radial_model_lm, newdata = this_radial_fake_data, interval = 'confidence'))-1
  # radial_predictions <- data.frame(radial_predictions)

  this_fe <- getfe(this_model)
  this_radial_fe <- getfe(this_radial_model)

  # fixed_effects <- mean(this_fe$effect)
  # radial_fixed_effects <- mean(this_radial_fe$effect)

  out <- this_fake_data
  # radial_out <- this_radial_fake_data

  out$fit <- predictions$fit + fixed_effects
  out$lwr <- predictions$lwr + fixed_effects
  out$upr <- predictions$upr + fixed_effects
  sim_list[[i]] <- out

  # radial_out$fit <- radial_predictions$fit + fixed_effects
  # radial_out$lwr <- radial_predictions$lwr + fixed_effects
  # radial_out$upr <- radial_predictions$upr + fixed_effects
  # radial_sim_list[[i]] <- radial_out
}
sim_data <- bind_rows(sim_list)
# radial_sim_data <- bind_rows(radial_sim_list)

# combine other info
predictions <- sim_data %>%
  mutate(absent = as.numeric(absent)) %>%
  filter(!is.na(fit))

simple <- predictions %>%
  group_by(strategy) %>%
  summarise(n = n(),
            actual_absences = sum(absent),
            predicted_absences = sum(fit, na.rm = TRUE)
            # actual = mean(absent, na.rm = TRUE),
            # predicted = mean(fit, na.rm = TRUE)
            ) %>%
  mutate(actual = actual_absences / n,
         predicted = predicted_absences / n)

zero <- predictions %>%
  filter(strategy == 'Zero') %>%
  mutate(year = as.numeric(format(date, '%Y'))) %>%
  group_by(year) %>%
  summarise(n = n(),
            actual_absences = sum(absent),
            predicted_absences = sum(fit, na.rm = TRUE),
            actual = mean(absent, na.rm = TRUE),
            predicted = mean(fit, na.rm = TRUE)) %>%
  mutate(avoided = predicted_absences - actual_absences)

# Scenario splot
pd <- simple
ggplot(data = pd,
       aes(x = strategy,
           y = value)) +
  geom_bar(stat = 'identity') +
  theme_maragra() +
  geom_text(aes(label = round(value * 100, digits = 2)), color = 'white',
            nudge_y = -0.01, 
            size = 7) +
  labs(x = 'Strategy',
       y = )
